Simulation for Correlation Motif

### 2017-09-05 analysis/Simulation.Rmd
wflow_publish("Simulation.Rmd")

---
title: "Simulation for Correlation Motif"
author: "Zhiwei Ma"
date: "8/30/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: "Simulation for Correlation Motif"
author: "Zhiwei Ma"
date: "8/30/2017"
output:
  html_document:
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=FALSE)
```
